Title: A proof-of-concept study

### 2022-01-08 paper.tex
update

  \begin{figure}
    \includegraphics[width=\columnwidth]{figures/fig__jetI5+ismSeed3-45deg_no-disk-stratified-ambient-Pres-Dens-Temp.png}
    \caption{Comparison of the cases with (left) and without (right) the dense disk.\
             In the both cases, the bipolar jets are injected at the origin along the $z=-y$ direction\
             with a constant 4-velocity of 0.6 for a duration of 1.2 Myr.
             The pressure (top), temperature (middle), and number density (bottom) slices\
             through the jet sources show that the dense disk not only helps the bubbles to align the disk normal\
             but also creates an under pressure, cold, and dense bubble in the most inner region.
             }
    \label{fig__jetI5+ismSeed3-45deg_no-disk-stratified-ambient-Pres-Dens-Temp}
  \end{figure}

>>>>

  \begin{figure}
    \includegraphics[width=\columnwidth]{figures/fig__jetI5+ismSeed3-45deg_no-disk-stratified-ambient-Pres-Dens-Temp.png}
    \caption{
             Comparison between the case with a clumpy (first column from left)\
             and a smooth disk (second) in a stratified atmosphere\
             shows that the density distribution of the dense disk has insignificant effect\
             on the overall dynamics of the bubbles. However, the bubbles with the smooth disk (third)\
             in an uniform atmosphere is spherical-shape,\
             suggesting the stratification facilitate bubbles elongation.\
             The rightmost column shows that the bubbles without disk is tilted even\
             in the stratified atmosphere, indicating dense disk is a crucial component\
             for axis-symmetric bubbles formation.\
             In all cases, bipolar jets are injected at the origin along $z=-y$ direction\
             for a duration of 1.2 Myr.
             The pressure (top), temperature (middle), and number density (bottom) slices\
             through jet sources show that the under pressure, cold, and dense bubbles (dashed box)\
             only appear if disk is present.
             }
    \label{fig__jetI5+ismSeed3-45deg_no-disk-stratified-ambient-Pres-Dens-Temp}
  \end{figure}
